Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area" \\ [1ex] \large Supplementary Information

### 2021-08-29 paper/main.tex
[DATALAD] auto-saved changes

@@

\todo[inline]{Since we did no analyses in surface space imo it makes more sense
    to explain the ``method'' to create the surface plots here in the
``Results''}

\todo[inline]{only Captions mention smoothing of union of PPAs; Volume FWHM was
2mm, Surface FWHM was 3mm; I changed that to 2mm; plotting scripts need to be
rerun}

\todo[inline]{Merge plots and adjust references here}

>>>>

\todo[inline]{The dataset (\citep{haeusler2021ppa}) should probably be cited here + datalad yada yada}

@@

### 2021-08-29 paper/suppl.tex
[DATALAD] auto-saved changes

% title has to be < 110 chars incl. spaces at the moment 106 Chars
\title{Processing of visual and non-visual naturalistic spatial information in
  the "parahippocampal place area"}

@@

\todo[inline]{Position der Abbildungen ist im kompilierten PDF maximal
verwirrend}
\todo[inline]{table of contents not necessary (?) but table of figures; see
    Guidelines: ``A table of contens should be included on the first page,
    listing the page number of each supplementary figure``}

@@

\section*{Supplementary Information}

\subsection*{Surface plots of individual results}

@@

\subsection*{Robustness of main findings across alternative contrasts}

@@

\subsection*{Incidental results}

@@

\subsection*{Control contrasts}

>>>>

\title{%
  Processing of visual and non-visual naturalistic spatial information in
the "parahippocampal place area" \\
[1ex] \large Supplementary Information}

@@

\todo[inline]{Position der Abbildungen ist im kompilierten PDF maximal
verwirrend}

\todo[inline]{I added table of contents & figure. s. Guidelines: ``A table of 
contens should be included on the first page, listing the page number of each 
supplementary figure``}

\tableofcontents

@@

\section{Surface plots of individual results}

@@

\section{Robustness of main findings across alternative contrasts}

@@

\section{Incidental results}

@@

\section{Control contrasts}
